### 2014-02-26 paper/concrete.tex
Theorem statement.
Signed-off-by: Edward Z. Yang <ezyang@cs.stanford.edu>

The operational semantics we have derived in the previous section
constitutes an abstract \emph{specification}: a semantics for which
non-interference is (obviously) true.  This specification can guide the
design of an information-flow calculus which would not be directly
derivable from our procedure, but is related to some such derivation.
For example, in our mini-ML language, the combined semantics requires
each thread to have a separate ML heap.  In an actual implementation, we
might like to only have a single heap, but disallowing the
passing of references between threads.  This restriction maintains a
correspondence between the abstract multiple heaps and the concrete
single heap.  As long as we don't add any extra transitions which directly
leak secret data, we might hope that non-interference follows
immediately.

However, when proving termination-\emph{sensitive} non-interference, we
cannot allow an arbitrary restrictions.  Consider a trivial state
machine as shown in Figure~\ref{fig:trivial-sm}, whose second projection
is classified secret.  With all three transitions, this language
fulfills termination-sensitive noninterference.  Furthermore, if the
dashed line is removed, the language continues to satisfy TSNI.
However, if any solid line is removed, however, the language fails TSNI.
Only \emph{some} transitions may be removed safely.

@@

In order to capture the condition with which transitions may be removed
safely, we require a novel, stronger variant of termination-sensitive
noninterference:

\begin{lemma}[Erased-transition/transition simulation (ETTS)]
    For any state |C|, if |erase l C ..-> delta|, then there exists a |C'| such that
    |erase l C' = delta| and |C .=> C'|.
\end{lemma}

Traditional TSNI is an easy corollary of this lemma.  \Red{Need to argue
this is provable!} Now we can state the result:

\begin{theorem}
    Suppose we have a abstract specification language $L$ with machine
    states $|C|$, evaluation relation $|.->|$, erasure function $|erasef l|$,
    and a proof that ETTS holds.

    Next, suppose we have a language $L'$ with machine states $|C'|$,
    evaluation relation $|.->|'$ and erasure function $|erasef l|'$.  We demand that this
    language be related to $L$ in the following way:

    \begin{itemize}
        \item There are functions $f : |C' -> C|$ and $f^{-1} : |C -> C'|$ which is functorial
            over $l$-equivalences: e.g. if $|C| \approx'_l |C'|$ then
            $f(|C|) \approx_l f(|C'|)$ and vice versa.
    \end{itemize}

    Then ETTS holds for language $L'$.
\end{theorem}

\begin{proof}
We need to show that for all choices of $|C1'|$, there exists a $|C2'|$ with
the desired properties.  We proceed by induction on the erased-transition.
There are two cases.  In the first case, there is a one-to-one correspondence
between reduction relations in

Our proof proceeds along the same lines as a traditional TSNI proof,
we simply must show \Red{Lemma~1} holds for our language.  We proceed by induction
over reduction derivations in the first step.

We have $ts'_1 \approx_l ts'_2$ and would like to show $f(ts'_1) \approx_l f(ts'_2)$;
this can be seen by expanding the definition of
\end{proof}

To provide a sense of how these conditions work, we give an example
use of these theorem:

\begin{theorem}
    The language described in Figure X satisfies termination sensitive non-interference.
\end{theorem}

\begin{code}
\end{code}

>>>>

The operational semantics we have derived in the previous section
constitutes an abstract \emph{specification}: a semantics for which
non-interference is (obviously) true.  This specification can guide the
design of an information-flow calculus which would not be directly
derivable from our procedure, but is related to some such derivation.
For example, in our mini-ML language, the combined semantics requires
each thread to have a separate ML heap.  In an actual implementation, we
might like to only have a single heap and disallow the passing of
references between threads.  This restriction maintains a correspondence
between the abstract multiple heaps and the concrete single heap.  We might
hope that we can prove noninterference for this new system by reusing
noninterference for the old system.

However, modifying operational rules poses a distinct problem for
preserving non-interference.  Consider a trivial state machine as shown
in Figure~\ref{fig:trivial-sm}, whose second projection is classified
secret.  With all three transitions, this language fulfills
termination-sensitive noninterference.  Furthermore, if the dashed line
is removed, the language continues to satisfy TSNI.  However, if any
solid line is removed, however, the language fails TSNI.

@@

The approach we will take is in two steps.  First, we sidestep the
restriction problem by demanding that the concrete implementation be
\emph{isomorphic} to the abstract specification, but perhaps having a different
runtime representation (a single heap) and some well-formedness
condition (every item on the heap only contains pointers from a single
location).  Isomorphism will preserve nonintereference, but it will also means all
transitions in the abstract language have to be implemented, including
undesirable transitions such as sending a pointer to another thread makes
the pointer dangling.  Next, we define a desugaring into this language
which adds dynamic checks, eliminating the possibility for these undesirable
transitions to be exercised.

\begin{theorem}[Isomorphism preserves termination sensitive non-interference]
    Consider a language \tar{L} with configurations |tc|, reduction
    relation \tar{|.->|} and erasure function \tar{|erasef l|} and a
    language \ifc{L} with configurations |ic|, reduction relation
    \ifc{|.->|} and erasure function \ifc{|erasef l|}.  We say that
    \tar{L} and \ifc{L} are isomorphic if there exist (total) functions
    $f : |tc -> ic|$ and $f^{-1} : |ic -> tc|$ such that $f \circ f^{-1}
    = id$, $f^{-1} \circ f^{-1} = id$, and that $f$ and $f^{-1}$ are
    functorial over $l$-equivalences (i.e. if $|tc|\ \tar{\approx_l}\
    |tc'|$ then $f(|tc|)\ \ifc{\approx_l}\ f(|tc'|)$ and vice-versa).
    Then if \ifc{L} satisfies termination sensitive non-interference,
    then \tar{L} satisfies termination sensitive non-interference.
\end{theorem}

\begin{proof}
    Easy application of TSNI \tar{L} by applying $f$
\end{proof}
